Full Article Review

### 2024-08-06 doc/reviews/daniel.qmd
Update daniel.qmd

<!-- Write your notes down here -->

@@

<!-- Write your notes down here -->

@@

<!-- Write your notes down here -->

@@

<!-- Write your notes down here -->

>>>>

## General themes

::: content-hidden
Look for what the paper is generally about and some basic overall themes and
topics in the paper.
:::

Tools to use.

## Type of paper

::: content-hidden
Is it a guide, community-building, an example of a workflow, etc.
:::

- example
- guide

## Other notes

::: content-hidden
What we found was interesting or what we'd like to share, discuss, or
present in the main scoping review paper.
:::

This paper is not much about open collaboration but more about which tools to use for open and reproducible research from start to finish of a project.

@@

## General themes

::: content-hidden
Look for what the paper is generally about and some basic overall themes and
topics in the paper.
:::

- community building
- social rules
- organization around the collaboration
- new comers

## Type of paper

::: content-hidden
Is it a guide, community-building, an example of a workflow, etc.
:::

- guide

## Other notes

::: content-hidden
What we found was interesting or what we'd like to share, discuss, or
present in the main scoping review paper.
:::

- Focus on building community: 1: be welcoming, 3. make governance explicit, 6. Develop forms of legitimate peripheral participation, 7. Make it easy for newcomers to get started.

@@

## General themes

::: content-hidden
Look for what the paper is generally about and some basic overall themes and
topics in the paper.
:::

- practical setup of collaboration

## Type of paper

::: content-hidden
Is it a guide, community-building, an example of a workflow, etc.
:::

- example

## Other notes

::: content-hidden
What we found was interesting or what we'd like to share, discuss, or
present in the main scoping review paper.
:::

Focus on large-scale collaboration in psychology, because of a main challenge of small samples sizes.

Project started in connection with a conference. First paper was a pilot. Main aim of the project is to provide infrastructure for latge-scale collaboration. Used mailing list to share information, then slack for discussions. Use Google docs for writing and documentation and github for code and data. Data analysis plans pre-registered at OSF. Have a website - good for newcomers and sharing info. Topic for research selected through voting. After organizing the data, they had a modelling challenge. Also discuss challenges. Main one was how to make decisions. Leadership team preferable. Also have author guidelines.

@@

## General themes

::: content-hidden
Look for what the paper is generally about and some basic overall themes and
topics in the paper.
:::

- data sharing

## Type of paper

::: content-hidden
Is it a guide, community-building, an example of a workflow, etc.
:::

- example

## Other notes

::: content-hidden
What we found was interesting or what we'd like to share, discuss, or
present in the main scoping review paper.
:::

- this paper is mostly about a database for sharing spinal injusry data. There are some points for how to improve sharing but not much about open collaboration
- open data commons for spinal injury
- Studies based on game theory suggest that data sharing might be beneficial if a collaborative approach is taken and data sharing is embraced as a community rather than by individuals
- key events for the collaboration to be possible: - introduction of FAIR principles, - update from funders, funding given to specific projects
- Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to share tabular data of research in the field of spinal cord injury
- Ain of the paper: to illustrate how members of research communities can work together toward the development of dedicated data sharing initiatives under the umbrella of FAIR
- clearly highlighted the value of the massive demonstration/work for beta testing the site to reveal unforeseen problems
- Moreover, participants pointed out the need for improving self-explanatory tutorials and help materials that would facilitate the learning experience for those who could not attend the workshop
- “Registered users can request to become ODC-SCI Community members with further approval by the Leadership team.” The most permissive account type is becoming an ODC-SCI Community member associated to an ODC-SCI lab, known as a Lab member
